Picky with peakpicking: assessing chromatographic peak quality with simple

### 2023-07-22 manuscript/manuscript.Rmd
Removing unnecessary header

---
title: 'Picky with peakpicking: assessing chromatographic peak quality with simple
  metrics in metabolomics'
author: "William Kumler, Bryna Hazelton, and Anitra Ingalls"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: template.docx
  pdf_document:
    latex_engine: xelatex
bibliography: refs.bib
---

>>>>

---
title: 'Picky with peakpicking: assessing chromatographic peak quality with simple
  metrics in metabolomics'
author: "William Kumler, Bryna Hazelton, and Anitra Ingalls"
output:
  word_document:
    reference_docx: template.docx
bibliography: refs.bib
---
